{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2018-02-09 sftrends_manu.Rnw
SCCWRP as primary address

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
  \\\\{\textit {\normalsize Current address: Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ \Sexpr{raw}
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

We thank the staff of the San Francisco Estuary Institute and the Delta Regional Monitoring Program.  All data are from the California Department of Water Resources Environmental Monitoring Program. We thank Larry Harding, Raphael Mazor, Yongshan Wan, and Susan Elizabeth George for providing comments on an earlier draft. This study was reviewed and approved for publication by the US EPA, National Health and Environmental Efects Research Laboratory. The authors declare no competing financial interest. The views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the US EPA.

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ \Sexpr{raw}
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

We thank the staff of the San Francisco Estuary Institute and the Delta Regional Monitoring Program.  All data are from the California Department of Water Resources Environmental Monitoring Program. We thank Larry Harding, Raphael Mazor, Yongshan Wan, and Susan Elizabeth George for providing comments on an earlier draft. The authors declare no competing financial interest.

### 2018-02-09 sftrends_manu.tex
submitted to ECSS
SCCWRP as primary address

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
  \\\\{\textit {\normalsize Current address: Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ Version Date:   Sun Jan 28 10:22:13 2018 -0800
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ Version Date:   Fri Feb 2 17:52:16 2018 -0800
	}
\date{}
\maketitle
\end{singlespace}
\clearpage
